---
title: "Exploring ggplot2"
author: "Maren Westermann"
output: html_document
---

#### Load the ggplot2 package
```{r}
library(ggplot2)
```


#### Explore the mtcars data frame with str()
```{r}
str(mtcars)
```

#### Execute the following command
```{r out.width = "50%"}
ggplot(mtcars, aes(x = cyl, y = mpg)) +
  geom_point()
```

#### Change the command below so that cyl is treated as factor
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = factor(cyl), y = mpg)) +
  geom_point()
```

#### A scatter plot has been made for you
```{r out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point()
```

#### Replace ___ with the correct column
```{r out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, color = disp)) +
  geom_point()
```

#### Replace ___ with the correct column
```{r out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, size = disp)) +
  geom_point()
```

#### Explore the diamonds data frame with str()
```{r}
str(diamonds)
```

#### Add geom_point() with +
```{r out.width = "50%"}
ggplot(diamonds, aes(x = carat, y = price)) + 
  geom_point()
```

#### Add geom_point() and geom_smooth() with +
```{r out.width = "50%"}
ggplot(diamonds, aes(x = carat, y = price)) + 
  geom_point() + 
  geom_smooth()
```

#### Copy the above command but show only the smooth line
```{r out.width = "50%"}
ggplot(diamonds, aes(x = carat, y = price)) +
  geom_smooth()
```

#### Copy the above command and assign the correct value to col in aes()
```{r out.width = "50%"}
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) +
  geom_smooth()
```

#### Keep the color settings from previous command. Plot only the points with argument alpha.
```{r out.width = "50%"}
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) +
  geom_point(alpha = 0.4)
```
