---
title: "Stats outside Geoms"
author: "Maren Westermann"
output: html_document
---

#### Load the ggplot2 package
```{r}
library(ggplot2)
```


## Preparations 

#### Display structure of mtcars
```{r}
str(mtcars)
```

#### Convert cyl and am to factors:
```{r}
mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$am <- as.factor(mtcars$am)
```

#### Define positions:
```{r}
posn.d <- position_dodge(width = 0.1)
posn.jd <- position_jitterdodge(jitter.width = 0.1, dodge.width = 0.2)
posn.j <- position_jitter(width = 0.2)
```

#### base layers:
```{r}
wt.cyl.am <- ggplot(mtcars, aes(x = cyl, y = wt, col = am, 
                                fill = am, group = am))
```


## Plotting variations 

#### Load Hmisc package
```{r}
library(Hmisc)
```

#### Plot 1: Jittered, dodged scatter plot with transparent points
```{r  out.width = "50%"}
wt.cyl.am +
  geom_point(position = posn.jd, alpha = 0.6)
```

#### Plot 2: Mean and SD - the easy way
```{r  out.width = "50%"}
wt.cyl.am +
  stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), position = posn.d)
```

#### Plot 3: Mean and 95% CI - the easy way
```{r  out.width = "50%"}
wt.cyl.am +
  stat_summary(fun.data = mean_cl_normal, position = posn.d)
```

#### Plot 4: Mean and SD - with T-tipped error bars - fill in ___
```{r  out.width = "50%"}
wt.cyl.am +
  stat_summary(geom = "point", fun.y = mean,
               position = posn.d) +
  stat_summary(geom = "errorbar", fun.data = mean_sdl,
               position = posn.d, fun.args = list(mult = 1), width = 0.1)
```


## Custom functions 

#### Create a vector
```{r}
xx <- (1:100)
```

#### Function to save range for use in ggplot
```{r}
gg_range <- function(x) {
  # Change x below to return the instructed values
  data.frame(ymin = min(x), # Min
             ymax = max(x)) # Max
}

gg_range(xx)
# Required output
#   ymin ymax
# 1    1  100
```

#### Function to Custom function
```{r}
med_IQR <- function(x) {
  # Change x below to return the instructed values
  data.frame(y = median(x), # Median
             ymin = quantile(x)[2], # 1st quartile
             ymax = quantile(x)[4])  # 3rd quartile
}

med_IQR(xx)
# Required output
#       y  ymin  ymax
# 25% 50.5 25.75 75.25
```


## Custom functions (2)

#### The base ggplot command, you don't have to change this
```{r}
wt.cyl.am <- ggplot(mtcars, aes(x = cyl,y = wt, col = am, fill = am, group = am))
```

#### Add three stat_summary calls to wt.cyl.am
```{r  out.width = "50%"}
wt.cyl.am +
  stat_summary(geom = "linerange", fun.data = med_IQR,
               position = posn.d, size = 3) +
  stat_summary(geom = "linerange", fun.data = gg_range,
               position = posn.d, size = 3,
               alpha = 0.4) +
  stat_summary(geom = "point", fun.y = median,
               position = posn.d, size = 3,
               col = "black", shape = "X")
```
