---
title: "Stats and Geoms"
author: "Maren Westermann"
output: html_document
---

#### Load the ggplot2 package
```{r}
library(ggplot2)
```


## Smoothing 

#### Explore the mtcars data frame with str()
```{r}
str(mtcars)
```

#### A scatter plot with LOESS smooth:
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() + 
  geom_smooth()
```

#### A scatter plot with an ordinary Least Squares linear model:
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() + 
  geom_smooth(method = "lm")
```

#### The previous plot, without CI ribbon:
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() + 
  geom_smooth(method = "lm", se = F)
```

#### The previous plot, without points:
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg)) + 
  geom_smooth(method = "lm", se = F)
```


## Grouping variables

#### Define cyl as a factor variable
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, col = factor(cyl))) +
  geom_point() +
  stat_smooth(method = "lm", se = F)
```

#### Complete the following ggplot command as instructed
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, col = factor(cyl))) +
  geom_point() +
  stat_smooth(method = "lm", se = F) + 
  stat_smooth(method = "lm", se = F, aes(group = 1))
```


## Modifying stat_smooth

#### Plot 1: change the LOESS span
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  # Add span below
  geom_smooth(se = F, span = 0.7)
```

#### Plot 2: Set the overall model to LOESS and use a span of 0.7
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, col = factor(cyl))) +
  geom_point() +
  stat_smooth(method = "lm", se = F) +
  # Change method and add span below
  stat_smooth(method = "loess", aes(group = 1),
              se = F, col = "black", span = 0.7)
```

#### Plot 3: Set col to "All", inside the aes layer of stat_smooth()
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, col = factor(cyl))) +
  geom_point() +
  stat_smooth(method = "lm", se = F) +
  stat_smooth(method = "loess",
              # Add col inside aes()
              aes(group = 1, col = "All"),
              # Remove the col argument below
              se = F, span = 0.7)
```

#### Load the RColorBrewer package
```{r}
library(RColorBrewer)
```

#### Plot 4: Add scale_color_manual to change the colors
```{r  out.width = "50%"}
myColors <- c(brewer.pal(3, "Dark2"), "black")
ggplot(mtcars, aes(x = wt, y = mpg, col = factor(cyl))) +
  geom_point() +
  stat_smooth(method = "lm", se = F, span = 0.75) +
  stat_smooth(method = "loess",
              aes(group = 1, col="All"),
              se = F, span = 0.7) +
  # Add correct arguments to scale_color_manual
  scale_color_manual("Cylinders", values = myColors)
```


## Modifying stat_smooth (2)

#### Load the car package
```{r}
library(car)
```

#### Plot 1: Jittered scatter plot, add a linear model (lm) smooth
```{r  out.width = "50%"}
ggplot(Vocab, aes(x = education, y = vocabulary)) +
  geom_jitter(alpha = 0.2) +
  stat_smooth(method = "lm", se = F)
```

#### Plot 2: Only lm, colored by year
```{r  out.width = "50%"}
ggplot(Vocab, aes(x = education, y = vocabulary, col = factor(year))) +
  stat_smooth(method = "lm", se = F) 
```

#### Plot 3: Set a color brewer palette 
```{r  out.width = "50%"}
ggplot(Vocab, aes(x = education, y = vocabulary, col = factor(year))) +
  stat_smooth(method = "lm", se = F) + 
  scale_color_brewer()
```

#### Plot 4: Add the group, specify alpha and size
```{r  out.width = "50%"}
ggplot(Vocab, aes(x = education, y = vocabulary, col = year, group = factor(year))) +
  stat_smooth(method = "lm", se = F, alpha = 0.6, size = 2) +
  scale_color_gradientn(colors = brewer.pal(9, "YlOrRd"))
```


## Quantiles 

#### Use stat_quantile instead of stat_smooth:
```{r  out.width = "50%"}
ggplot(Vocab, aes(x = education, y = vocabulary, col = year, group = factor(year))) +
  stat_quantile(alpha = 0.6, size = 2) +
  scale_color_gradientn(colors = brewer.pal(9,"YlOrRd"))
```

#### Set quantile to 0.5:
```{r  out.width = "50%"}
ggplot(Vocab, aes(x = education, y = vocabulary, col = year, group = factor(year))) +
  stat_quantile(alpha = 0.6, size = 2, quantiles = 0.5) +
  scale_color_gradientn(colors = brewer.pal(9,"YlOrRd"))
```


## Sum 

#### Plot with linear and loess model
```{r}
p <- ggplot(Vocab, aes(x = education, y = vocabulary)) +
  stat_smooth(method = "loess", aes(col = "x"), se = F) +
  stat_smooth(method = "lm", aes(col = "y"), se = F) +
  scale_color_discrete("Model", labels = c("x" = "LOESS", "y" = "lm"))
```

#### Add stat_sum
```{r  out.width = "50%"}
p + stat_sum()
```

#### Add stat_sum and set size range
```{r  out.width = "50%"}
p + stat_sum() + 
  scale_size(range = c(1,10))
```