---
title: "Bar plots"
author: "Maren Westermann"
output: html_document
---

#### Load the ggplot2 package
```{r}
library(ggplot2)
```

#### Change cyl inside mtcars to a factor
```{r}
mtcars$cyl <- as.factor(mtcars$cyl) 
```

#### Change am inside mtcars to a factor
```{r}
mtcars$am <- as.factor(mtcars$am)
```


## Bar plots (1)

#### Base layers
```{r}
m <- ggplot(mtcars, aes(x = cyl, y = wt))
```

#### Draw dynamite plot
```{r  out.width = "50%"}
m +
  stat_summary(fun.y = mean, geom = "bar", fill = "skyblue") +
  stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1)
```


## Bar plots (2)

#### Base layers
```{r}
m <- ggplot(mtcars, aes(x = cyl,y = wt, col = am, fill = am))
```

#### Plot 1: Draw dynamite plot
```{r  out.width = "50%"}
m +
  stat_summary(fun.y = mean, geom = "bar") +
  stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1)
```

#### Plot 2: Set position dodge in each stat function
```{r  out.width = "50%"}
m +
  stat_summary(fun.y = mean, geom = "bar", position = "dodge") +
  stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), 
               geom = "errorbar", width = 0.1, position = "dodge")
```

#### Set your dodge posn manually
```{r}
posn.d <- position_dodge(0.9)
```

#### Plot 3:  Redraw dynamite plot
```{r  out.width = "50%"}
m +
  stat_summary(fun.y = mean, geom = "bar", position = posn.d) +
  stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1, position = posn.d)
```


## Bar plots (3)

#### Load the readr package
```{r}
library(readr)
```

#### Load the mtcars.cyl dataset 
```{r}
mtcars.cyl <- read_delim("../mtcars_cyl.txt", delim = "/")
```

#### Base layers
```{r}
m <- ggplot(mtcars.cyl, aes(x = cyl, y = wt.avg))
```

#### Plot 1: Draw bar plot
```{r  out.width = "50%"}
m + geom_bar(stat = "identity", fill = "skyblue")
```

#### Plot 2: Add width aesthetic
```{r  out.width = "50%"}
m + geom_bar(aes(width = prop), stat = "identity", fill = "skyblue")
```

#### Plot 3: Add error bars
```{r  out.width = "50%"}
m + geom_bar(aes(width = prop), stat = "identity", fill = "skyblue") +  
  geom_errorbar(aes(ymin  =wt.avg - sd, ymax = wt.avg + sd), width = 0.1)
```