---
title: "All about aesthetics"
author: "Maren Westermann"
output: html_document
---

#### Load the ggplot2 package
```{r}
library(ggplot2)
```

#### Change cyl inside mtcars to a factor
```{r}
mtcars$cyl <- as.factor(mtcars$cyl)
```

#### Map mpg to x and cyl to y
```{r  out.width = "50%"}
ggplot(mtcars, aes(mpg, cyl)) +
  geom_point()
```

#### Reverse: Map cyl to x and mpg to y
```{r  out.width = "50%"}
ggplot(mtcars, aes(cyl, mpg)) +
  geom_point()
```

#### Map wt to x, mpg to y and cyl to col
```{r  out.width = "50%"}
ggplot(mtcars, aes(wt, mpg, color = cyl)) +
  geom_point()
```

#### Change shape and size of the points in the above plot
```{r  out.width = "50%"}
ggplot(mtcars, aes(wt, mpg, color = cyl)) +
  geom_point(shape = 1, size = 4)
```


#### Change am inside mtcars to a factor
```{r}
mtcars$am <- as.factor(mtcars$am)
```

#### am and cyl are factors, wt is numeric
```{r}
class(mtcars$am)
class(mtcars$cyl)
class(mtcars$wt)
```

#### Map cyl to fill
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, fill = cyl)) +
  geom_point(shape = 1, size = 4)
```

#### Change shape and alpha of the points in the above plot
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, fill = cyl)) +
  geom_point(shape = 21, size = 4, alpha = 0.6)
```

#### Map am to col in the above plot
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, fill = cyl, col = am)) +
  geom_point(shape = 21, size = 4, alpha = 0.6)
```


#### Map cyl to size
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, size = cyl)) +
  geom_point() 
```

#### Map cyl to alpha
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, alpha = cyl)) +
  geom_point()
```

#### Map cyl to shape 
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, shape = cyl)) +
  geom_point()
```

#### Map cyl to label
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, label = cyl)) +
  geom_text() 
```