---
title: "All about attributes and going all out"
author: "Maren Westermann"
output: html_document
---

#### Load the ggplot2 package
```{r}
library(ggplot2)
```

#### Change cyl inside mtcars to a factor
```{r}
mtcars$fcyl <- as.factor(mtcars$cyl) 
```

## All about attributes
#### Define a hexadecimal color
```{r}
my_color <- "#4ABEFF"
```

#### First scatter plot, with col aesthetic:
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, color = fcyl)) + 
  geom_point()
```

#### Plot 1, but set col attributes in geom layer:
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, color = fcyl)) +  
  geom_point(color = my_color)
```

#### Plot 2, with fill instead of col aesthetic, plus shape and size attributes in geom layer.
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, fill = fcyl)) +  
  geom_point(size = 10, shape = 23, color = my_color)
```

#### Expand to draw points with alpha 0.5
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, fill = cyl)) + 
  geom_point(alpha = 0.5)
```


#### Expand to draw points with shape 24 and color yellow
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, fill = cyl)) + 
  geom_point(shape = 24, color = "yellow")
```


#### Expand to draw text with label rownames(mtcars) and color red
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, fill = cyl)) + 
  geom_text(label = rownames(mtcars), color = "red")
```


## Going all out
#### Map mpg onto x, qsec onto y and factor(cyl) onto col
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = mpg, y = qsec, color = factor(cyl))) + 
  geom_point()
```

#### Add mapping: factor(am) onto shape
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = mpg, y = qsec, color = factor(cyl), shape = factor(am))) + 
  geom_point()
```

#### Add mapping: (hp/wt) onto size
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = mpg, y = qsec, color = factor(cyl), shape = factor(am), size = (hp/wt))) + 
  geom_point()
```