---
title: "Coordinates Layer"
author: "Maren Westermann"
output: html_document
---

#### Load the ggplot2 package
```{r}
library(ggplot2)
```


## Zooming in 

#### Basic ggplot() command, coded for you
```{r}
p <- ggplot(mtcars, aes(x = wt, y = hp, col = factor(am))) + 
  geom_point() + geom_smooth()
```

#### Add scale_x_continuous
```{r  out.width = "50%"}
p + scale_x_continuous(limits = c(3,6), expand = c(0,0))
```

#### The proper way to zoom in:
```{r  out.width = "50%"}
p + coord_cartesian(xlim = c(3,6))
```


## Aspect ratio

#### Complete basic scatter plot function
```{r}
base.plot <- ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, col = Species)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = F)
```

#### Plot base.plot: default aspect ratio
```{r  out.width = "50%"}
base.plot
```

#### Fix aspect ratio (1:1) of base.plot
```{r  out.width = "50%"}
base.plot + coord_equal()
```


## Pie charts 

#### Create stacked bar plot: thin.bar
```{r}
thin.bar <- ggplot(mtcars, aes(x = 1, fill = factor(cyl))) +
  geom_bar()
```

#### Convert thin.bar to pie chart
```{r  out.width = "50%"}
thin.bar + coord_polar(theta = "y")
```

#### Create stacked bar plot: wide.bar
```{r}
wide.bar <- ggplot(mtcars, aes(x = 1, fill = factor(cyl))) +
  geom_bar(width = 1)
```

#### Convert wide.bar to pie chart
```{r  out.width = "50%"}
wide.bar + coord_polar(theta = "y")
```
