---
title: "Facets Layer"
author: "Maren Westermann"
output: html_document
---

#### Load the ggplot2 package
```{r}
library(ggplot2)
```


## Facets: the basics 

#### Basic scatter plot
```{r}
p <- ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point()
```

#### Separate rows according to transmission type, am
```{r  out.width = "50%"}
p + facet_grid(. ~ am)
```

#### Separate columns according to cylinders, cyl
```{r  out.width = "50%"}
p + facet_grid(cyl ~ .)
```

#### Separate by both columns and rows 
```{r  out.width = "50%"}
p + facet_grid(cyl ~ am)
```


## Many variables 

#### Load the RColorBrewer package
```{r}
library(RColorBrewer) 
```

#### Code to create the cyl_am col and myCol vector
```{r}
mtcars$cyl_am <- paste(mtcars$cyl, mtcars$am, sep = "_")
myCol <- rbind(brewer.pal(9, "Blues")[c(3,6,8)],
               brewer.pal(9, "Reds")[c(3,6,8)])
```

#### Basic scatter plot, add color to scale: 
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, col = cyl_am)) +
  geom_point() +
  scale_color_manual(values = myCol)
```

#### Facet according on rows and columns. 
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, col = cyl_am)) +
  geom_point() +
  scale_color_manual(values = myCol) + 
  facet_grid(gear ~ vs)
```

#### Add more variables 
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = wt, y = mpg, col = cyl_am, size = disp)) +
  geom_point() +
  scale_color_manual(values = myCol) + 
  facet_grid(gear ~ vs)
```


## Dropping levels 

#### Load the readr package
```{r}
library(readr)
```

#### Load the mamsleep dataset
```{r}
mamsleep <- read_delim("../mamsleep.txt", delim = "/")
```

#### Basic scatter plot
```{r  out.width = "50%"}
ggplot(mamsleep, aes(x = time, y = name, col = sleep)) + 
  geom_point()
```

#### Facet rows accoding to vore
```{r  out.width = "50%"}
ggplot(mamsleep, aes(x = time, y = name, col = sleep)) + 
  geom_point() + 
  facet_grid(vore ~ .)
```

#### Specify scale and space arguments to free up rows
```{r  out.width = "50%"}
ggplot(mamsleep, aes(x = time, y = name, col = sleep)) + 
  geom_point() + 
  facet_grid(vore ~ ., scale = "free_y", space = "free_y")
```

