---
title: "qplot and wrap-up"
author: "Maren Westermann"
output: html_document
---

#### Load the ggplot2 package
```{r}
library(ggplot2)
```


## Using qplot

#### The old way (shown)
```{r  out.width = "50%"}
plot(mpg ~ wt, data = mtcars) # formula notation
with(mtcars, plot(wt, mpg)) # x, y notation
```

#### Using ggplot:
```{r  out.width = "50%"}
ggplot(mtcars, aes(wt, mpg)) +
  geom_point()
```

#### Using qplot:
```{r  out.width = "50%"}
qplot(wt, mpg, data = mtcars)
```


## Using aesthetics

#### Categorical variable mapped onto size:
#### cyl
```{r  out.width = "50%"}
qplot(wt, mpg, data = mtcars, size = factor(cyl))
```

#### gear
```{r  out.width = "50%"}
qplot(wt, mpg, data = mtcars, size = factor(gear))
```

#### Continuous variable mapped onto col:
#### hp
```{r  out.width = "50%"}
qplot(wt, mpg, data = mtcars, col = hp)
```

#### qsec
```{r  out.width = "50%"}
qplot(wt, mpg, data = mtcars, color = qsec)
```


## Choosing geoms 

#### qplot() with x only
```{r  out.width = "50%"}
qplot(factor(cyl), data = mtcars)
```

#### qplot() with x and y
```{r  out.width = "50%"}
qplot(factor(cyl), factor(vs), data = mtcars)
```

#### qplot() with geom set to jitter manually
```{r  out.width = "50%"}
qplot(factor(cyl), factor(vs), data = mtcars, geom = "jitter")
```


#### "Basic" dot plot, with geom_point():
```{r  out.width = "50%"}
ggplot(mtcars, aes(factor(cyl), wt, col = factor(am))) +
  geom_point(position = position_jitter(0.2, 0))
```

#### "True" dot plot, with geom_dotplot():
```{r  out.width = "50%"}
ggplot(mtcars, aes(factor(cyl), wt, fill = factor(am))) +
  geom_dotplot(binaxis = "y", stackdir = "center")
```

#### qplot with geom "dotplot", binaxis = "y" and stackdir = "center"
```{r  out.width = "50%"}
qplot(
  factor(cyl), wt,
  data = mtcars,
  fill = factor(am),
  geom = "dotplot",
  binaxis = "y",
  stackdir = "center"
)
```


## Chicken weight 

#### Check out the head of ChickWeight
```{r}
head(ChickWeight)
```

#### Basic line plot
```{r  out.width = "50%"}
ggplot(ChickWeight, aes(x = Time, y = weight)) +
  geom_line(aes(group = Chick))
```

#### Take plot 2, map Diet onto col.
```{r  out.width = "50%"}
ggplot(ChickWeight, aes(x = Time, y = weight, color = Diet)) +
  geom_line(aes(group = Chick))
```

#### Take plot 3, add geom_smooth()
```{r  out.width = "50%"}
ggplot(ChickWeight, aes(x = Time, y = weight, color = Diet)) +
  geom_line(aes(group = Chick, alpha = 0.3)) + 
  geom_smooth(lwd = 2, se = F)
```


## Titanic 

#### Load the readr package
```{r}
library(readr)
```

#### Load the titanic dataset
```{r}
titanic <- read_delim("../titanic.txt", delim = "/")
```

#### Change Sex inside titanic to a factor
```{r}
titanic$Sex <- as.factor(titanic$Sex)
```

#### Check the structure of titanic
```{r}
str(titanic)
```

#### Use ggplot() for the first instruction
```{r  out.width = "50%"}
ggplot(titanic, aes(x = Pclass, fill = Sex)) +
  geom_bar(position = "dodge")
```

#### Plot 2, add facet_grid() layer
```{r  out.width = "50%"}
ggplot(titanic, aes(x = Pclass, fill = Sex)) +
  geom_bar(position = "dodge") + 
  facet_grid(. ~ Survived)
```

#### Define an object for position jitterdodge, to use below
```{r}
posn.jd <- position_jitterdodge(0.5, 0, 0.6)
```

#### Plot 3, but use the position object from instruction 4
```{r  out.width = "50%"}
ggplot(titanic, aes(x = Pclass, y = Age, col = Sex)) +
  geom_point(position = posn.jd, size = 3, alpha = 0.5) + 
  facet_grid(. ~ Survived)
```