---
title: "Bar plots"
author: "Maren Westermann"
output: html_document
---

#### Load the ggplot2 package
```{r}
library(ggplot2)
```


## Histograms

#### Make a univariate histogram
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram()
```

#### Plot 1, plus set binwidth to 1 in the geom layer
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram(binwidth = 1)
```

#### Plot 2, plus MAP ..density.. to the y aesthetic (i.e. in a second aes() function)
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram(aes(y= ..density..),binwidth = 1)
```

#### plot 3, plus SET the fill attribute to "####377EB8"
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram(aes(y= ..density..),binwidth = 1, fill = "#377EB8")
```


## Position

#### Change cyl inside mtcars to a factor
```{r}
mtcars$cyl <- as.factor(mtcars$cyl) 
```

#### Change am inside mtcars to a factor
```{r}
mtcars$am <- as.factor(mtcars$am)
```

#### Draw a bar plot of cyl, filled according to am
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = cyl, fill = am)) +
  geom_bar()
```

#### Change the position argument to stack
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = cyl, fill = am)) +
  geom_bar(position = "stack")
```

#### Change the position argument to fill
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = cyl, fill = am)) +
  geom_bar(position = "fill")
```

#### Change the position argument to dodge
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = cyl, fill = am)) +
  geom_bar(position = "dodge")
```


## Overlapping bar plots

#### Define posn_d with position_dodge()
```{r}
posn_d <- position_dodge(width = 0.2)
```

#### Change the position argument to posn_d
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = cyl, fill = am)) +
  geom_bar(position = posn_d)
```

#### Use posn_d as position and adjust alpha to 0.6
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = cyl, fill = am)) +
  geom_bar(position = posn_d, alpha = 0.6)
```


## Overlapping histograms

#### A basic histogram, add coloring defined by cyl
```{r  out.width = "50%"}
ggplot(mtcars, aes(mpg, fill = cyl)) +
  geom_histogram(binwidth = 1)
```

#### Change position to identity
```{r  out.width = "50%"}
ggplot(mtcars, aes(mpg, fill = cyl)) +
  geom_histogram(binwidth = 1, position = "identity")
```

#### Change geom to freqpoly (position is identity by default)
```{r  out.width = "50%"}
ggplot(mtcars, aes(mpg, col = cyl)) +
  geom_freqpoly(binwidth = 1, position = "identity")
```


## Bar plots with color ramp 

#### Example of how to use a brewed color palette
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = cyl, fill = am)) +
  geom_bar() +
  scale_fill_brewer(palette = "Set1")
```

#### Load the car package
```{r}
library(car)
```

#### Use str() on Vocab to check out the structure
```{r}
str(Vocab)
```

#### Plot education on x and vocabulary on fill
#### Use the default brewed color palette
```{r  out.width = "50%"}
ggplot(Vocab, aes(x = factor(education), fill = factor(vocabulary))) + 
  geom_bar(position = "fill") + 
  scale_fill_brewer(palette = "Set1")
```

#### Load the RColorBrewer package
```{r}
library(RColorBrewer)
```

#### Definition of a set of blue colors
```{r}
blues <- brewer.pal(9, "Blues") # from the RColorBrewer package
```

#### Make a color range using colorRampPalette() and the set of blues
```{r}
blue_range <- colorRampPalette(blues)
```

#### Use blue_range to adjust the color of the bars, use scale_fill_manual()
```{r  out.width = "50%"}
ggplot(Vocab, aes(x = factor(education), fill = factor(vocabulary))) +
  geom_bar(position = "fill") +
  scale_fill_manual(values = blue_range(11))
```


## Overlapping histograms(2)

#### Basic histogram plot command
```{r  out.width = "50%"}
ggplot(mtcars, aes(mpg)) +
  geom_histogram(binwidth = 1)
```

#### Plot 1, Expand aesthetics: am onto fill
```{r  out.width = "50%"}
ggplot(mtcars, aes(mpg, fill = am)) +
  geom_histogram(binwidth = 1)
```

#### Plot 2, change position = "dodge"
```{r  out.width = "50%"}
ggplot(mtcars, aes(mpg, fill = am)) +
  geom_histogram(binwidth = 1, position = "dodge")
```

#### Plot 3, change position = "fill"
```{r  out.width = "50%"}
ggplot(mtcars, aes(mpg, fill = am)) +
  geom_histogram(binwidth = 1, position = "fill")
```

#### Plot 4, plus change position = "identity" and alpha = 0.4
```{r  out.width = "50%"}
ggplot(mtcars, aes(mpg, fill = am)) +
  geom_histogram(binwidth = 1, position = "identity", alpha = 0.4)
```

#### Plot 5, plus change mapping: cyl onto fill
```{r  out.width = "50%"}
ggplot(mtcars, aes(mpg, fill = cyl)) +
  geom_histogram(binwidth = 1, position = "identity", alpha = 0.4)
```