---
title: "Line plots"
author: "Maren Westermann"
output: html_document
---

#### Load the ggplot2 package
```{r}
library(ggplot2)
```


## Line plots

#### Print out head of economics
```{r}
head(economics)
```

#### Plot unemploy as a function of date using a line plot
```{r  out.width = "50%"}
ggplot(economics, aes(x = date, y = unemploy)) +
  geom_line()
```

#### Adjust plot to represent the fraction of total population that is unemployed
```{r  out.width = "50%"}
ggplot(economics, aes(x = date, y = unemploy/pop)) +
  geom_line()
```


## Periods of recession

#### Load the recess dataset 
```{r}
load("../recess.RData")
```

#### Expand the following command with geom_rect() to draw the recess periods
```{r  out.width = "50%"}
ggplot(economics, aes(x = date, y = unemploy/pop)) +
  geom_rect(data = recess,
            aes(xmin = begin, xmax = end, ymin = -Inf, ymax = +Inf),
            inherit.aes = FALSE, fill = "red", alpha = 0.2) +
  geom_line()
```


## Multiple time series

#### Load the fish dataset 
```{r}
load("../fish.RData")
```

#### Check the structure as a starting point
```{r}
str(fish.species)
```

#### Recreate the plot shown on the right
```{r  out.width = "50%"}
ggplot(fish.tidy, aes(x = Year, y = Capture, col = Species)) +
  geom_line()
```
