---
title: "Scatter plots"
author: "Maren Westermann"
output: html_document
---

#### Load the ggplot2 package
```{r}
library(ggplot2)
```

#### Change cyl inside mtcars to a factor
```{r}
mtcars$cyl <- as.factor(mtcars$cyl) 
```

#### Shown in the viewer:
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = cyl, y = wt)) +
  geom_point()
```

#### Solutions:
#### 1 - With geom_jitter()
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = cyl, y = wt)) +
  geom_jitter()
```

#### 2 - Set width in geom_jitter()
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = cyl, y = wt)) +
  geom_jitter(width = 0.1)
```

#### 3 - Set position = position_jitter() in geom_point() ()
```{r  out.width = "50%"}
ggplot(mtcars, aes(x = cyl, y = wt)) +
  geom_point(position = position_jitter(0.1))
```


#### Load the car package
```{r}
library(car)
```

#### Examine the structure of Vocab
```{r}
str(Vocab)
```

#### Basic scatter plot of vocabulary (y) against education (x). Use geom_point()
```{r  out.width = "50%"}
ggplot(Vocab, aes(x = education, y = vocabulary)) + 
  geom_point()
```

#### Use geom_jitter() instead of geom_point()
```{r  out.width = "50%"}
ggplot(Vocab, aes(x = education, y = vocabulary)) + 
  geom_jitter()
```

#### Using the above plotting command, set alpha to a very low 0.2
```{r  out.width = "50%"}
ggplot(Vocab, aes(x = education, y = vocabulary)) + 
  geom_jitter(alpha = 0.2)
```

#### Using the above plotting command, set the shape to 1
```{r  out.width = "50%"}
ggplot(Vocab, aes(x = education, y = vocabulary)) + 
  geom_jitter(alpha = 0.2, shape = 1)
```
